```{r}
# Step 1
library(tidyverse)
library(DBI)
library(RMySQL)
dbConnection <- dbConnect(RMySQL::MySQL( ), user = 'root', password='CjordanG05', dbname = 'petstore4', host ='localhost')
sqlString1 <- "select * , month(saledate) AS month, day(saledate) AS day
FROM
        ((((`sale`
        JOIN `customer` ON ((`sale`.`CustomerID` = `customer`.`CustomerID`)))
        JOIN `saleitem` ON ((`saleitem`.`SaleID` = `sale`.`SaleID`)))
        JOIN `merchandise` ON ((`saleitem`.`ItemID` = `merchandise`.`ItemID`)))
        JOIN `city` ON ((`customer`.`CityID` = `city`.`CityID`)))"
q_Results1 <- dbGetQuery(dbConnection, sqlString1)
str(q_Results1 )
```
```{r}
# Step 2
colnames(q_Results1)    # identify duplicates
sqlString2 <- "select customer.customerID, firstname, lastname, phone, address, city.city, city.state, city.zipcode, merchandise.itemid, description, category, sale.saleID,
saledate, month(saledate) as month, day(saledate) as day, employeeid, salestax, saleitem.quantity, saleprice
FROM
        ((((`sale`
        JOIN `customer` ON ((`sale`.`CustomerID` = `customer`.`CustomerID`)))
        JOIN `saleitem` ON ((`saleitem`.`SaleID` = `sale`.`SaleID`)))
        JOIN `merchandise` ON ((`saleitem`.`ItemID` = `merchandise`.`ItemID`)))
        JOIN `city` ON ((`customer`.`CityID` = `city`.`CityID`)))"
q_Results2 <- dbGetQuery(dbConnection, sqlString2)
view(q_Results2)
```
```{r}
#Step 3
q_Results3 <- mutate(q_Results2, subtotal = quantity*saleprice)
summarize(q_Results3, TotalSales = sum(subtotal))
view(q_Results3)
```
```{r}
#Step 4
by_category <- group_by(q_Results3, category)
category_total <- summarize(by_category, TotalSales = sum(subtotal))
view(category_total)
```
```{r}
# Step 5
arrange(category_total, desc(TotalSales))
view(category_total)
```
```{r}
# Step 6
category_count <- summarize(by_category, ItemsSold = sum(quantity))
view(category_count)
```
```{r}
# Step 7
arrange(category_count, desc(ItemsSold))
view(category_count)
```
```{r}
# Step 7
by_customer <- group_by(q_Results3, customerID, firstname, lastname)
customer_total <- summarize(by_customer, TotalPurchases = sum(subtotal), ItemsSold = sum(quantity), AverageItem = TotalPurchases/ItemsSold)
view(customer_total)
```
```{r}
# Step 8
MaySales <- filter(q_Results3, month == 5)
arrange(MaySales, (saledate))
view(MaySales)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
